Space is the Place: Effects of Continuous Spatial Structure on Analysis of Population Genetic Data

### 2019-12-05 ms/spaceness.tex

%%%%%%%%%%%%%
\subsection{Summary Statistics}
We calculated the site frequency spectrum and a set of 18 summary statistics (Table \ref{table:sumstats}) from 60 diploid individuals sampled from the final generation of each simulation using the python package scikit-allel \citep{Miles2017}. 
Statistics included common single-population summaries including mean pairwise divergence ($\pi$), inbreeding coefficient ($F_{IS}$), and Tajima's $D$, 
as well (motivated by \citet{Rousset1997}'s results)
the correlation coefficient between the logarithm of the spatial distance and the proportion of identical base pairs across pairs of individuals. 
% as an isolation-by-distance regression of genetic distance ($D_{xy}$) against the logarithm of geographic distance analogous to \citet{Rousset1997}'s approach, which we summarized as

>>>>

%%%%%%%%%%%%%
\subsection{Summary Statistics}
We calculated the site frequency spectrum and a set of 18 summary statistics (Table \ref{table:sumstats}) from 60 diploid individuals sampled from the final generation of each simulation using the python package scikit-allel \citep{Miles2017}. 
Statistics included common single-population summaries including mean pairwise divergence ($\pi$), inbreeding coefficient ($F_{IS}$), and Tajima's $D$, 
as well as (motivated by \citet{Rousset1997}'s results)
the correlation coefficient between the logarithm of the spatial distance and the proportion of identical base pairs across pairs of individuals. 
% as an isolation-by-distance regression of genetic distance ($D_{xy}$) against the logarithm of geographic distance analogous to \citet{Rousset1997}'s approach, which we summarized as
